---
title: "Figuring Out how to do this"
description: |
  How to solve this problem?
author:
  - name: Ben Arancibia
    url: {}
date: 09-10-2020
output:
  distill::distill_article:
    self_contained: false
categories:
  - philly
  - tidyverse
preview: reticulated_python.png
twitter:
  site: "@bcarancibia"
  creator: "@bcarancibia"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

So I have been trying figure out how best to do create a repeatable process for scraping nba data and use it in Rstats. There are a lot of guides online on how to scrape basketball reference data and that was the initial way I was thinking about this problem. Create a bunch of functions and then from those functions create a package. I started down that path and was able to create a quick scraping script, which was not that difficult. 

```{r, include = TRUE, error=FALSE}
library(tidyverse)
library(rvest)
library(janitor)

url <- "https://www.basketball-reference.com/leagues/NBA_2019_totals.html"
stats <- url %>% 
  read_html() %>% 
  html_table() %>% 
  .[[1]]


stats <- stats %>% 
  clean_names() %>%        
  dplyr::filter(!player=="Player") %>%  
  mutate_at(vars(-c(player,tm,pos)),as.numeric) %>%
  mutate_at(vars(-c(player,tm,pos)), funs(replace(., is.na(.), 0))) %>% 
  as_tibble()
str(stats)

stats <- stats %>% 
  group_by(player) %>% 
  slice(1) %>% 
  ungroup()

head(stats)

```


After looking at this, I saw that basketball reference under their use of data and terms of use. Looking through really quickly, it looks like I should not use this for scraping data frequently or building a set of functions on top of their existing data. As a result, I am going to look at using the NBA API, which does not have existing prebuilt R Libraries to download quickly. Some exist, but they are not maintained well and lack a lot of documentation making them hard to use. This might be a good excuse to try to use [reticulate] (https://rstudio.github.io/reticulate/)
and try out merging existing python libraries with r functionality. 
